\thetitle

### 2021-05-19 writing/discussion.tex
Update plots and discussion of results with new data from re-run
Add draft threat subsection about natural-biased scenarios

The results of the experiment suggests a number of high-level conclusions about
blame strategies in the gradual typed world.  First, run-time type checks have a
large positive impact, regardless of whether these checks assign blame or throw
plain exceptions.  Second, error messages with blame assignments are more
helpful than those without. The results also indicate, though, that blame is not
critical in a majority of cases, and therefore they suggest investigating
whether blame tracking is worth the performance cost.  Third, the Natural
approach fares better than the Transient approach, but only by a small margin.
Since Natural offers complete and sound path-based blame (i.e. it blames all and only those components
that are relevant to a type impedance mismatch) while Transient offers
incomplete but sound heap-based blame~\citep{gfd-oopsla-2019}, the results call
for a study concerning the relative strengths of the two models of blame.
Fourth, given that Transient's sound but shallow run-time type checks do not
seem to hamper debugging, a version of the Natural semantics of Typed Racket
that disables some of its wrappers may offer an answer to the well-known
performance issues of Natural~\citep{gtnffvf-jfp-2019}.  Fifth, given that both
modes of the Transient rational programmer are equally successful and that
Transient-last produces shorter trails, Reticulated Python could limit the size
of blame sequences to the last few entries to reduce its serious performance
problems (see below).

@@

>>>>

The results of the experiment suggests a number of high-level conclusions about
blame strategies in the gradual typed world.  First, run-time type checks have a
large positive impact, regardless of whether these checks assign blame or throw
plain exceptions.  Second, error messages with blame assignments are more
helpful than those without. The results also indicate, though, that blame is not
critical in a majority of cases, and therefore they suggest investigating
whether blame tracking is worth the performance cost.  Third, the Natural
approach fares better than the Transient approach, but only by a small margin.
Since Natural offers complete and sound path-based blame (i.e. it blames all and only those components
that are relevant to a type impedance mismatch) while Transient offers
incomplete but sound heap-based blame~\citep{gfd-oopsla-2019}, the results call
for a study concerning the relative strengths of the two models of blame.
Fourth, given that Transient's sound but shallow run-time type checks do not
seem to hamper debugging, a version of the Natural semantics of Typed Racket
that disables some of its wrappers may offer an answer to the well-known
performance issues of Natural~\citep{gtnffvf-jfp-2019}.

@@

%% -----------------------------------------------------------------------------
\subsection{Threat: Is the Definition of Interesting Scenarios Reasonable?} \label{sec:threat:erasure-bias}

Section~\ref{sub:mutate-interesting} defines criteria for interesting mutations,
one of which limits the scenarios under consideration to those with mistakes
detectable by Erasure. In other words, the experiment only considers the utility
of blame when no checking at all is necessary to detect a problem. In reality,
checking is necessary to detect some mistakes, and it is possible that blame has
more or less to offer for these kinds of mistakes. If that is the case, then the
results of the experiment on a population of scenarios including such mistakes
should be quite different.

The authors have collected preliminary data that suggests this difference may be
large. In particular, the data comes from running the experiment with a
population including any scenario detectable by Natural, regardless of the other
semantics; the population therefore also includes scenarios where Transient or
Erasure may not even detect the mistake.
%% While that detection disparity reflects reality in that such mistakes can be made in practice, it also biases the population to favor Natural in those new scenarios where Transient and Erasure have no chance to succeed.
Under this broader population of scenarios, the preliminary experimental results
suggest that Natural blame may be much more useful than all of the other modes.
